---
title: "Chapter 4"
output: html_document
date: "2023-08-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load Packages
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(meta)
library(PRISMAstatement)
library(skimr)
library(MASS)
library(ggpubr)
```
```{r}
setwd("~/Desktop/Chapter 4")
photo <- read.csv("observations_2022.csv")
summary(photo)
```
```{r}
photo <- photo %>%
  filter(common_name != "Human")
photo <- photo %>%
  filter(common_name != "Human-Camera Trapper")
photo <- photo %>%
  filter(common_name != "Domestic Dog")
photo <- photo %>%
  filter(common_name != "Vehicle")
photo <- photo %>%
  dplyr::filter(common_name != "Insect")
photo <- photo %>%
  dplyr::filter(common_name != "Animal")
photo <- photo %>%
  dplyr::filter(common_name != "Bird")
photo <- photo %>%
  filter(common_name != "No CV Result")
  
count.hit <- photo %>%
  count(animal.hit) %>%
  na.omit()
summary(count.hit)
### 2022 Had a 5.88% catch rate
```
```{r}
### Animal Observations by Site_Code
animals_by_sitecode <- photo%>%
  group_by(site_code, microsite, common_name) %>%
  summarise(captures = sum(animal.hit), n = n())
animals_by_sitecode <- animals_by_sitecode %>%
  filter(common_name != "Blank") 
```

```{r}
### Animal observations by Site
animals_by_site <- photo %>% group_by(site,microsite,common_name) %>% summarise(captures = sum(animal.hit))
animals_by_site <- animals_by_site %>% filter(common_name != "Blank")

```

```{r}
### Animal observations by Density
animals_by_density <- photo %>% group_by(microsite,common_name) %>% summarise(captures = sum(animal.hit))
animals_by_density <- animals_by_density %>% filter(common_name != "Blank")  %>% filter(common_name != "No CV Result")
```
```{r}
### Total Observations 2022
Total_Observations <- photo %>% group_by(common_name) %>% summarise(total = sum(animal.hit)) %>% filter(common_name != "Blank")  %>% filter(common_name != "No CV Result")
```

```{r}
density_obvs <- merge(animals_by_density, Total_Observations, all = TRUE)
density_obvs$percent_presence <- density_obvs$captures/density_obvs$total
```

```{r}
### Percent proportion Figure
plot1 <- ggplot(density_obvs, aes(common_name, percent_presence, fill = microsite)) + geom_bar(stat = "identity") + coord_flip() + theme_classic() + scale_x_discrete(limits=rev) + xlab("Species") + ylab("Percent Proportion") + labs(fill = "Microsite")
plot1 + scale_fill_manual(values = c("#009900", "#0066cc"))
```
```{r}
library(emmeans)
m1 <- glm(total ~ microsite*common_name, family = "poisson", data = density_obvs)
anova(m1, test = "Chisq")
e1 <- emmeans(m1, pairwise~common_name)
e1
```
```{r}
animals_density <- photo %>% group_by(site_code,microsite,plot, shrub_density, common_name) %>% summarise(captures = sum(animal.hit))
animals_density <- animals_density %>% filter(common_name != "Blank") %>% filter(common_name != "No CV Result")
```

### All current PCOA code for 2022 only
```{r}
### PCA
library(vegan)
library(ape) ### For PCOA
pca_data <- animals_density ### Created new df for pca data
pca_data <- pca_data %>%
  spread(common_name, captures) %>%
  ungroup() %>%
  dplyr::select(-site_code, -microsite, -plot) %>%
  replace(is.na(.),0)
dim(pca_data)

env <- read.csv("environment.csv") ### Drop Tecopa open 1, Tecopa open 4, since they have no animal observations.
dim(env)

m01 <- adonis(pca_data ~ microsite*shrub_density, data = env)
m01

dist <- vegdist(pca_data, species = "bray")
res <- pcoa(dist)
p1 <- as.data.frame(res$vectors)%>%
  dplyr::select(Axis.1, Axis.2) %>%
  bind_cols(env,.)

ggplot(p1, aes(Axis.1, Axis.2, group = microsite)) +
  geom_point(aes(color = microsite)) +
  geom_text(aes(label=plot), hjust = 0, vjust = 0, check_overlap = TRUE, nudge_x = 0.01)+
  scale_color_brewer(palette = "Set1") +
  labs(color = "", subtitle = "labels denote plot identity")

m02 <- betadisper(dist, env$microsite)
m02
anova(m02)
permutest(m02,pairwise = TRUE, permutations = 99)
m02.HSD <- TukeyHSD(m02)
boxplot(m02)
```
```{r}
m03 <- betadisper(dist, env$shrub_density)
m03
anova(m03)
permutest(m03,pairwise = TRUE, permutations = 99)
m03.HSD <- TukeyHSD(m03)
boxplot(m03)
```
```{r}
m04 <- betadisper(dist, env$site)
m04
anova(m04)
permutest(m04,pairwise = TRUE, permutations = 99)
m04.HSD <- TukeyHSD(m04)
boxplot(m04)
```
### 2023 Data
```{r}
photo_2023 <- read.csv("observations_2023.csv")
summary(photo_2023)

photo_2023 <- photo_2023 %>%
  filter(common_name != "Human")
photo_2023 <- photo_2023 %>%
  filter(common_name != "Human-Camera Trapper")
photo_2023 <- photo_2023 %>%
  filter(common_name != "Domestic Dog")
photo_2023 <- photo_2023 %>%
  filter(common_name != "Vehicle")
photo_2023 <- photo_2023 %>%
  dplyr::filter(common_name != "Insect")
photo_2023 <- photo_2023 %>%
  dplyr::filter(common_name != "Animal")
photo_2023 <- photo_2023 %>%
  dplyr::filter(common_name != "Bird")
photo_2023 <- photo_2023 %>%
  dplyr::filter(common_name != "No CV Result")
  
count.hit_2023 <- photo_2023 %>%
  count(animal.hit) %>%
  na.omit()
summary(count.hit_2023)

### 2023 had a 0.28% capture rate
```
```{r}
### Animal Observations by Site_Code
animals_by_sitecode_2023 <- photo_2023%>%
  group_by(site_code, microsite, common_name) %>%
  summarise(captures = sum(animal.hit), n = n())
animals_by_sitecode_2023 <- animals_by_sitecode_2023 %>%
  filter(common_name != "Blank") %>% filter(common_name != "No CV Result") 
```
```{r}
### Animal observations by Site 2023
animals_by_site_2023 <- photo_2023 %>% group_by(site,microsite,common_name) %>% summarise(captures = sum(animal.hit))
animals_by_site_2023 <- animals_by_site_2023 %>% filter(common_name != "Blank") %>% filter(common_name != "No CV Result") 

```
```{r}
### Animal observations by Density
animals_by_density_2023 <- photo_2023 %>% group_by(microsite,common_name) %>% summarise(captures = sum(animal.hit))
animals_by_density_2023 <- animals_by_density_2023 %>% filter(common_name != "Blank")  %>% filter(common_name != "No CV Result")
```

```{r}
### Total Observations 2023
Total_Observations_2023 <- photo_2023 %>% group_by(common_name) %>% summarise(total = sum(animal.hit)) %>% filter(common_name != "Blank")  %>% filter(common_name != "No CV Result")
```

```{r}
density_obvs_2023 <- merge(animals_by_density_2023, Total_Observations_2023, all = TRUE)
density_obvs_2023$percent_presence <- density_obvs_2023$captures/density_obvs_2023$total
```

```{r}
### Percent proportion Figure
plot2 <- ggplot(density_obvs_2023, aes(common_name, percent_presence, fill = microsite)) + geom_bar(stat = "identity") + coord_flip() + theme_classic() + scale_x_discrete(limits=rev) + xlab("Species") + ylab("Percent Proportion") + labs(fill = "Microsite")
plot2 + scale_fill_manual(values = c("#009900", "#0066cc"))
```

```{r}
m2<- glm(total ~ microsite*common_name, family = "poisson", data = density_obvs_2023)
anova(m2, test = "Chisq")
e2 <- emmeans(m2, pairwise~common_name)
e2
```

```{r}
animals_density_2023 <- photo_2023 %>% group_by(site_code,microsite,plot, shrub_density, common_name) %>% summarise(captures = sum(animal.hit))
animals_density_2023 <- animals_density_2023 %>% filter(common_name != "Blank")
```

```{r}
pca_data_2023 <- animals_density_2023 ### Created new df for pcoa data
pca_data_2023 <- pca_data_2023 %>%
  spread(common_name, captures) %>%
  ungroup() %>%
  dplyr::select(-site_code, -microsite, -plot) %>%
  replace(is.na(.),0)
dim(pca_data_2023)

env_2023 <- read.csv("environment_2023.csv") ### Drop Tecopa open 1, Tecopa open 4, since they have no animal observations.
dim(env)

model01 <- adonis(pca_data_2023 ~ microsite*shrub_density, data = env_2023)
model01

dist_2023 <- vegdist(pca_data_2023, species = "bray")
res_2023 <- pcoa(dist_2023)
p2 <- as.data.frame(res_2023$vectors)%>%
  dplyr::select(Axis.1, Axis.2) %>%
  bind_cols(env_2023,.)

ggplot(p2, aes(Axis.1, Axis.2, group = microsite)) +
  geom_point(aes(color = microsite)) +
  geom_text(aes(label=plot), hjust = 0, vjust = 0, check_overlap = TRUE, nudge_x = 0.01)+
  scale_color_brewer(palette = "Set1") +
  labs(color = "", subtitle = "labels denote plot identity")

model02 <- betadisper(dist_2023, env_2023$microsite)
model02
anova(model02)
permutest(model02,pairwise = TRUE, permutations = 99)
model02.HSD <- TukeyHSD(model02)
boxplot(model02)
```

```{r}
model03 <- betadisper(dist_2023, env_2023$shrub_density)
model03
anova(model03)
permutest(model03,pairwise = TRUE, permutations = 99)
model03.HSD <- TukeyHSD(model03)
boxplot(model03)
```
```{r}
model04 <- betadisper(dist_2023, env_2023$site)
model04
anova(model04)
permutest(model04,pairwise = TRUE, permutations = 99)
model04.HSD <- TukeyHSD(model04)
boxplot(model04)
```
### From running the community compositions both in 2022 and 2023 it seems the community compositions across densities, microsites, and sites are all somewhat similar with no significant differences.

## Run PCOAs for both years combined!
```{r}
photo_final <- read.csv("observations_final.csv")
summary(photo_final)
```
```{r}
photo_final <- photo_final %>%
  filter(common_name != "Human")
photo_final <- photo_final %>%
  filter(common_name != "Human-Camera Trapper")
photo_final <- photo_final %>%
  filter(common_name != "Domestic Dog")
photo_final <- photo_final %>%
  filter(common_name != "Vehicle")
photo_final <- photo_final %>%
  dplyr::filter(common_name != "Insect")
photo_final <- photo_final %>%
  dplyr::filter(common_name != "Animal")
photo_final <- photo_final %>%
  dplyr::filter(common_name != "Bird")
  
count.hit_final <- photo_final %>%
  count(animal.hit) %>%
  na.omit()
summary(count.hit_final)
# Wow we have a 1.489% capture rate for the project!
```

```{r}
### Animal Observations by Site_Code
animals_by_sitecode_final <- photo_final%>%
  group_by(site_code, microsite, common_name) %>%
  summarise(captures = sum(animal.hit), n = n())
animals_by_sitecode_final <- animals_by_sitecode_final %>%
  filter(common_name != "Blank") %>% filter(common_name != "No CV Result") 
```

```{r}
animals_by_site_final <- photo_final %>% group_by(site,microsite,common_name) %>% summarise(captures = sum(animal.hit))
animals_by_site_final <- animals_by_site_final %>% filter(common_name != "Blank") %>% filter(common_name != "No CV Result")
```
```{r}
animals_by_density_final<- photo_final %>% group_by(microsite,common_name) %>% summarise(captures = sum(animal.hit))
animals_by_density_final <- animals_by_density_final %>% filter(common_name != "Blank")  %>% filter(common_name != "No CV Result")
```
```{r}
Total_Observations_final <- photo_final %>% group_by(common_name) %>% summarise(total = sum(animal.hit)) %>% filter(common_name != "Blank")  %>% filter(common_name != "No CV Result") %>% filter(common_name != "Mammal")
```

```{r}
density_obvs_final <- merge(animals_by_density_final, Total_Observations_final, all = TRUE) %>% filter(common_name != "Mammal")
density_obvs_final$percent_presence <- density_obvs_final$captures/density_obvs_final$total
```

```{r}
### Percent proportion Figure
plot3 <- ggplot(density_obvs_final, aes(common_name, percent_presence, fill = microsite)) + geom_bar(stat = "identity") + coord_flip() + theme_classic() + scale_x_discrete(limits=rev) + xlab("Species") + ylab("Percent Proportion") + labs(fill = "Microsite")
plot3 <-plot3 + scale_fill_manual(values = c("#009900", "#0066cc"))
```

```{r}
m3<- glm(total ~ microsite*common_name, family = "poisson", data = density_obvs_final)
anova(m3, test = "Chisq")
e3 <- emmeans(m3, pairwise~common_name)
e3
```

```{r}
animals_density_final <- photo_final %>% group_by(site_code,microsite,plot, shrub_density, common_name) %>% summarise(captures = sum(animal.hit))
animals_density_final <- animals_density_final %>% filter(common_name != "Blank") %>% filter(common_name != "Mammal")
```

```{r}
pca_data_final <- animals_density_final ### Created new df for pca data
pca_data_final <- pca_data_final %>%
  spread(common_name, captures) %>%
  ungroup() %>%
  dplyr::select(-site_code, -microsite, -plot) %>%
  replace(is.na(.),0)
dim(pca_data_final)

env_final <- read.csv("environment_final.csv") ### Drop Tecopa open 1, Tecopa open 4, since they have no animal observations.
dim(env_final)

model010 <- adonis(pca_data_final ~ microsite*shrub_density, data = env_final)
model010

dist_final <- vegdist(pca_data_final, species = "bray")
res_final <- pcoa(dist_final)
p02 <- as.data.frame(res_final$vectors)%>%
  dplyr::select(Axis.1, Axis.2) %>%
  bind_cols(env_final,.)

pcoa_final <- ggplot(p02, aes(Axis.1, Axis.2, group = microsite)) +
  geom_point(aes(color = microsite)) +
  geom_text(aes(label=plot), hjust = 0, vjust = 0, check_overlap = TRUE, nudge_x = 0.01)+
  scale_color_brewer(palette = "Set1") + theme_classic() + theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5), axis.text = element_text(size = 10)) +
  labs(color = "Shrub Density")
pcoa_final


model020 <- betadisper(dist_final, env_final$microsite)
model020
anova(model020)
permutest(model020,pairwise = TRUE, permutations = 99)
model020.HSD <- TukeyHSD(model020)
boxplot(model020)
```
```{r}
model030 <- betadisper(dist_final, env_final$shrub_density)
model030
anova(model030)
permutest(model030,pairwise = TRUE, permutations = 99)
model030.HSD <- TukeyHSD(model030)
boxplot(model030)
```
```{r}
### Shows a significant difference between community composition of tested sites (Carrizo -> Cuyama -> Tecopa)
model040 <- betadisper(dist_final, env_final$site)
model040
anova(model040)
permutest(model040,pairwise = TRUE, permutations = 99)
model040.HSD <- TukeyHSD(model040)
boxplot(model040)
```
### Temperature Data 2022
```{r}
Temp_2022 <- read_csv("Temp Data 2022.csv")

Temp_2022_final <- Temp_2022 %>%
  group_by(site_code, microsite) %>%
  summarise(mean_temp = mean(temp), max_temp = max(temp))
```
```{r}
###Ground Temp Data
Ground_Temp_2022 <- read_csv("Gradient Density Datasheet 2022.csv")
Ground_Temp_2022_final <- Ground_Temp_2022 %>%
  group_by(site_code, microsite) %>%
  summarise(mean_ground_temp = mean(ground_temp), mean_humidity = mean(RH), max_humidity = max(RH), max_ground_temp = max(ground_temp)) 
### Combine this with new_data
```

```{r}
### Aridity Data
aridity <- read_csv("regional_sites_2022.csv")
aridity <- aridity %>%
 dplyr::select(site_code, aridity)
```



```{r}
final_2022<- photo%>%
  group_by(site, site_code, year, microsite, plot, shrub_density, common_name) %>%
  summarise(captures = sum(animal.hit), n = n())
final_2022 <- final_2022 %>%
  filter(common_name != "Blank")%>% filter(common_name != "No CV Result")

density_simple <- final_2022 %>%
  group_by(site, site_code, year, microsite, plot, shrub_density) %>%
  summarise(animals = sum(captures), richness = n()) %>%
 rename(microsite_number = 'plot')

#write.csv(density_simple, file = "density_simple_fixed.csv") Output density simple because it does not include the sites with 0 observations
density_simple_fixed <- read.csv("density_simple_fixed.csv")
density_simple_fixed <- density_simple_fixed[,-1]

```

```{r}
### This is for 2022 evenness
vegan_data <- animals_density ### Created new df for pca data
vegan_data <- vegan_data %>%
  spread(common_name, captures) %>%
  ungroup() %>%
  replace(is.na(.),0)


evenness_data <- vegan_data %>%
  group_by(site_code, microsite) %>%
  summarize(across(5:29, ~diversity(., index = "shannon")))
evenness_data <- na.omit(evenness_data)

evenness_data <- evenness_data %>%
  mutate(Average_Evenness = rowMeans(across(5:26)))

evenness_data <- evenness_data %>%
  dplyr::select(site_code, microsite, Average_Evenness) 
### Join evenness_data with density_simple data
new_data <- inner_join(density_simple_fixed, evenness_data, by = c("site_code", "microsite"))

### Combine new data with logger temp data from 2022
new_data <- inner_join(new_data, Temp_2022_final,by = c("site_code", "microsite"))

### Need to add ground temperature from hand recordings then 2022 is ready!
new_data <- inner_join(new_data, Ground_Temp_2022_final, by = c("site_code", "microsite"))

### Combine all data with aridity data of the sites we have
new_data <- inner_join(new_data, aridity, by = c("site_code"))

### 2022 data is now cleaned and ready to go
```


```{r}
### Clean up 2023 data so it can be properly combined with 2022 data

final_2023<- photo_2023%>%
  group_by(site, site_code, year, microsite, plot, shrub_density, common_name) %>%
  summarise(captures = sum(animal.hit), n = n())
density_simple_2023 <- final_2023 %>%
  group_by(site, site_code, year, microsite, plot, shrub_density) %>%
  summarise(animals = sum(captures), richness = n()) %>%
 rename(microsite_number = 'plot')

write.csv(density_simple_2023, file = "density_simple_fixed_2023.csv")


### This is for 2023 evenness
vegan_data_2023 <- animals_density_2023 ### Created new df for pca data
vegan_data_2023 <- vegan_data_2023 %>%
  spread(common_name, captures) %>%
  ungroup() %>%
  replace(is.na(.),0)

evenness_data_2023 <- vegan_data_2023 %>%
  group_by(site_code, microsite) %>%
  summarize(across(5:27, ~diversity(., index = "shannon")))
evenness_data_2023 <- na.omit(evenness_data_2023)

evenness_data_2023 <- evenness_data_2023 %>%
  mutate(Average_Evenness = rowMeans(across(5:24)))
evenness_data_2023 <- evenness_data_2023 %>%
  dplyr::select(site_code, microsite, Average_Evenness) 
new_data_2023 <- inner_join(density_simple_2023, evenness_data_2023, by = c("site_code", "microsite"))

new_data_2023$site_code <- gsub("Tecopa_Shrub", "Tecopa_shrub", new_data_2023$site_code)
new_data_2023$site_code <- gsub("Tecopa_Open", "Tecopa_open", new_data_2023$site_code)

### Follow same steps as above 2022 data clean up. Start with logger temp, then ground temp, then aridity.

### Combine new_data_2023 to Temp_2023
Temp_2023 <- read_csv("Temp Data 2023.csv") %>% filter(!(temp > 50)) %>% filter(!(temp < -47))

Temp_2023_final <- Temp_2023 %>%
  group_by(site_code, microsite) %>%
  summarise(mean_temp = mean(temp), max_temp = max(temp))


new_data_2023 <- inner_join(new_data_2023, Temp_2023_final, by = c("site_code", "microsite"))

### Combine Ground Temp Data from 2023
Ground_Temp_2023 <- read_csv("Gradient Density Datasheet 2023.csv")
Ground_Temp_2023_final <- Ground_Temp_2023 %>%
  group_by(site_code, microsite, microsite_number) %>%
  summarise(mean_ground_temp = mean(ground_temp), mean_humidity = mean(RH), max_humidity = max(RH), max_ground_temp = max(ground_temp)) 

new_data_2023 <- inner_join(new_data_2023, Ground_Temp_2023_final, by = c("site_code", "microsite", "microsite_number"))

### Aridity data is already set up from 2022 data
new_data_2023 <- inner_join(new_data_2023, aridity, by = c("site_code"))

### 2023 Data is now cleaned and ready to be combined with 2022 data
```

```{r}
final_data <- rbind(new_data, new_data_2023)
```

### All Data is combined now into one clean dataframe that can be used to generate figures and statistics (Use final_data)

### Stats for Shrub Density

```{r}
library(ggpubr)
shapiro.test(final_data$animals)
ggqqplot(final_data$animals)

```

```{r}
### Abundance
model1 <- glm(animals~shrub_density*site*year+aridity, family = "gaussian", data = final_data)
model1


anova(model1, test = "Chisq")

e2 <- emmeans(model1, pairwise~site*year)
e2
### Emmeans contrast shows that during the drought year (2022) areas that are typically less arid such as Cuyama, when experiencing drought, animals are more likely to associate at higher densities than open areas. The is true for Cuyama and Carrizo which are much less arid than Tecopa. These Stats I THINK look good.
### When you look at 2023 there is no significance when contrasting the sites. Since this was NOT a drought year, but rather a superbloom, then we can conclude that the animals were not entirely dependent on the shrubs to survive, hence why there is no significant differences between the sites.
```
```{r}
shapiro.test(final_data$richness)
ggqqplot(final_data$richness)
### Richness Stats
model2 <- glm(richness~shrub_density*site*year +aridity, family = "gaussian", data = final_data)
model2
anova_results2 <- aov(model2, test = "Chisq")
summary(anova_results2)
e3 <- emmeans(model2, pairwise~site*year)
e3  ### Ok now this all works.
```
```{r}
ggqqplot(final_data$Average_Evenness)
### Evenness
model3 <- glm(Average_Evenness~shrub_density*site*year + aridity, family = "gaussian", data = final_data)
model3
anova_results3 <- aov(model3, test = "Chisq")
summary(anova_results3)
e4 <- emmeans(model3, pairwise~site*year)
e4  ### Need to double check emmeans it does not match the figure
```
### Data Viz
```{r}
### All below in chunk are by site

### Abundance vs Density
abundance <- ggplot(final_data, aes(shrub_density, animals, color = site)) +
  geom_point(size = 0.5) +
  facet_wrap(~year)+
  scale_color_brewer(palette = "Set1") + theme_classic() + theme(legend.position = "none") + theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5),legend.position = "none", legend.title = element_blank(), axis.text = element_text(size = 10)) +
  geom_smooth(method = lm, se = TRUE) + theme(axis.title.x = element_blank()) + labs(tag = "A")+
  labs(x = "Shrub Density (Individuals per 20m radius)", y = "Animal Abundance")
abundance 

richness <- ggplot(final_data, aes(shrub_density, richness, color = site)) +
  geom_point(size = 0.5) +
  facet_wrap(~year)+
  scale_color_brewer(palette = "Set1") + theme_classic() +  theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5), axis.text = element_text(size = 10)) +
  geom_smooth(method = lm, se = TRUE) + theme(axis.title.x = element_blank()) + labs(tag = "B")+
  labs(x = "Shrub Density (Individuals per 20m radius)", y = "Species Richness", color = "Region")
richness

Evenness <- ggplot(final_data, aes(shrub_density, Average_Evenness, color = site)) +
  geom_point(size = 0.5) +
  facet_wrap(~year)+
  scale_color_brewer(palette = "Set1") + theme_classic() + theme(legend.position = "none") + theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5),legend.position = "none", legend.title = element_blank(), axis.text = element_text(size = 10)) +
  geom_smooth(method = lm, se = TRUE) +  labs(tag = "C")+
  labs(x = expression("Shrub Density per " * 20 * m^2), y = "Mean Evenness")
Evenness
library(patchwork)
density_plot <- abundance/richness/Evenness
density_plot
```
### Stats for Average Temperature
```{r}
### Abundance and temperature
model4 <- glm(animals~mean_temp*site*year*mean_humidity, family = "gaussian", data = final_data) 
model4
anova_results4 <- aov(model4, test = "Chisq")
summary(anova_results4)
e5 <- emmeans(model4, pairwise~site*year)
e5
```
```{r}
### Richness and temperature
model5 <- glm(richness~mean_temp*site*year*mean_humidity, family = "gaussian", data = final_data) 
model5
anova_results5 <- aov(model5, test = "Chisq")
summary(anova_results5)
e6 <- emmeans(model5, pairwise~site*year)
e6
```
```{r}
### Evenness and temperature
model6 <- glm(Average_Evenness~mean_temp*site*year*mean_humidity, family = "gaussian", data = final_data) 
model6
anova_results6 <- aov(model6, test = "Chisq")
summary(anova_results6)
e7 <- emmeans(model6, pairwise~site*year)
e7
```

```{r}
### Ambient Temperature Plots

### Plots of temp might look super ugly.

abundance_temp <- ggplot(final_data, aes(mean_temp, animals)) +
  geom_point(size = 0.5) +
  facet_wrap(~year, scales = "free")+ 
  scale_color_brewer(palette = "Set1") +
  labs(x = "Average Temperature (C)", y = "Animal Abundance") + theme_classic() + theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5),legend.position = "none",legend.title = element_blank(), axis.text = element_text(size = 10)) +
  geom_smooth(method = lm, se = TRUE) + theme(axis.title.x = element_blank()) + labs(tag = "A")
abundance_temp

richness_temp <- ggplot(final_data, aes(mean_temp, richness)) +
  geom_point(size = 0.5) +
  facet_wrap(~year, scales = "free")+
  scale_color_brewer(palette = "Set1") + theme(axis.title.x = element_blank()) + labs(tag = "B")+ theme_classic() + theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5),legend.position = "none",legend.title = element_blank(), axis.text = element_text(size = 10)) +
  geom_smooth(method = lm, se = TRUE) +
  labs(x = "Average Temperature (C)", y = "Species Richness") + theme(axis.title.x = element_blank())
richness_temp

evenness_temp <- ggplot(final_data, aes(mean_temp, Average_Evenness)) +
  geom_point(size = 0.5) +
  facet_wrap(~year, scales = "free")+
  scale_color_brewer(palette = "Set1") + theme_classic() + theme(legend.position = "none") + theme(text = element_text(size = 12), panel.border = element_rect(color = "black", fill = NA, size = 1.5),legend.position = "none", legend.title = element_blank(), axis.text = element_text(size = 10)) +
  geom_smooth(method = lm, se = TRUE) +  labs(tag = "C")+
  labs(x = expression("Mean Temperature (°C)"), y = "Mean Evenness")
evenness_temp

temp_plot <- abundance_temp/richness_temp/evenness_temp
temp_plot
```



### Final Figures for Publication

```{r}
### Figure 1: Abundance, Richness, Evenness vs Shrub Density
density_plot
### Figure 2: Abundance, Richness, Evenness vs Average Temperature
temp_plot
### Figure 3: PCOA of Communities
pcoa_final
### Figure 4: Percent Proportion of Vertebrate species
plot3
```
```{r}
#write.csv(final_data, file = "Final Data.csv")
```

